Readme for Muir and Angert

### 2017-10-13 README.Rmd
Update readme

# card-cline
Grow with the flow: a latitudinal cline in physiology is associated with more variable precipitation in *Erythranthe cardinalis*. In Press at *Journal of Evolutionary Biology*.

>>>>

# card-cline
[Grow with the flow: a latitudinal cline in physiology is associated with more variable precipitation in *Erythranthe cardinalis*](https://dx.doi.org/10.1111/jeb.13184). *Journal of Evolutionary Biology*.
